%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Staff Analyst} % Job title
    {US Army} % Organization
    {Fairfield, CA} % Location
    {Aug. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyze inventory to identify operational problems and 
                communicate said issues to key stakeholders in the process. 
                }
        \item {Assist company commander with supply chain planning to facilitate smooth execution. 
                }
        \item {Create alarms and monitors units' inventory flow using Microsoft VBA and GCSS-A.}
        {}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Multifamily Investment Analyst} % Job title
    {Marcus and Millichap} % Organization
    {Palo Alto, CA} % Location
    {Oct. 2020 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Underwrote more than 200 multifamily properties based on location and returns.}
        \item {Directed meetings with potential clients to communicate sales 
                objectives and pricing expectations. 
                }
        \item {Tracked projects, proposals, and leads within Salesforce.}
        {}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tax Intern} % Job title
    {KPMG, LLP} % Organization
    {Sacramento, CA} % Location
    {Jun. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed multiple engagements and assignments while simultaneously learning in house software.}
        \item {Processed tax documentation and work papers for investment funds, trusts, and pension plans.}
        \item {Assisted in filing client’s federal, state, and international compiled returns during busy season.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
